TacticToe: Learning to Prove with Tactics

### 2018-02-20 tactictoe_jv.tex

When \tactictoe finds a proof of a goal $g_{root}$, it returns a search tree
$\mathfrak{T}$ where the root node containing $g_{root}$ is solved.
In order to transform this search tree into a proof script, we need to extract
the tactics that contributed to the proof and combine them using tactic
combinators.

@@

The extracted proof script of $\mathfrak{T}$ is $P_{goal}(g_{root})$.
We minimally improve it by subtituting \texttt{THENL} by \texttt{THEN} when the
list of goals is a singleton and removing \texttt{THENL []} during the
extraction phase.
Further post-processing such as
eliminating unnecessary tactics and theorems has been developed and
improve the user experience greatly~\cite{DBLP:conf/sefm/Adams15}.

>>>>

When \tactictoe finds a proof of an initial goal, it returns a search tree
$\mathfrak{T}$ where the root node containing the initial goal is solved.
In order to transform this search tree into a proof script, we need to extract
the tactics that contributed to the proof and combine them using tactic
combinators.

@@

The extracted proof script of $\mathfrak{T}$ is $P_{goal}(g_{root})$.
We minimally improve it by subtituting \texttt{THENL} by \texttt{THEN} when the
list of goals is a singleton and removing \texttt{THENL []} during the
extraction phase.
Further post-processing such as
eliminating unnecessary tactics and theorems has been developed and
improves the user experience greatly~\cite{DBLP:conf/sefm/Adams15}.
